---
title: "Visualisation of Findings"
output: html_document
---

# Visualisation
This Rmd file will contain the compilation and visualisation of results

## Load the overall results
```{r}
library(dplyr)
library(purrr)
library(stringr)
library(ggplot2)

load("mc_ratio_var5_sim1000.rdata")
load("mcratio_5var_scene10_50.rdata")
load("mcratio_10var_scene10_75.rdata")
load("mcratio_25var_scene10_100.rdata")

```
## Breaking down each rdata file
```{r}
str(mcratio_5var_scene10_50)
```
### Combine all the files into one main DF, calling it df_master

```{r}
load_reshape <- function(file_path, num_var, scenario10_num_var){
  name <- load(file_path)
  df_list <- get(name)
  df_combined <- map_df(
    names(df_list),
    function(model_name) {
      df <- df_list[[model_name]]
      df_renamed <- df %>%
        rename_with(
          ~ str_replace(., paste0(model_name, "_"), ""),  # remove "modelname_" prefix
          ends_with("_mc")
        )
      
      df_renamed %>%
        mutate(
          model = model_name,
          num_var = num_var,
          scenario10_num_var = scenario10_num_var
        )
    }
  )
  
  return(df_combined)
}

df_5_50 <- load_reshape(
  file_path = "mcratio_5var_scene10_50.rdata",
  num_var = 5,
  scenario10_num_var = 50
)

df_10_75 <- load_reshape(
  file_path = "mcratio_10var_scene10_75.rdata",
  num_var = 10,
  scenario10_num_var = 75
)

df_25_100 <- load_reshape(
  file_path = "mcratio_25var_scene10_100.rdata",
  num_var = 25,
  scenario10_num_var = 100
)

df_master <- bind_rows(df_5_50, df_10_75, df_25_100)
```

```{r}
str(df_master)
```

### Plotting the Bias by Scenario and Model for each number of variables
```{r}
df_master <- df_master %>%
  mutate(scenario = factor(scenario)) %>%
  mutate(model = recode(model,
                         madr = "MADR",
                         sis_lasso = "SiS Lasso",
                         backward_selection = "Backward Selection",
                         sis_glider = "SiS GLiDeR",
                         adaptive_lasso = "Adaptive Lasso",
                         glider = "GLiDeR",
                         rlasso = "rLasso"))

unique_numvar <- unique(df_master$num_var)

for (nv in unique_numvar) {
  df_temp <- df_master %>% filter(num_var == nv)
    p <- ggplot(df_temp, aes(x = scenario, y = bias_mc, color = model, group = model)) +
    geom_line() +
    geom_point() +
    scale_y_continuous(limits = c(-4,4))+
    theme_minimal() +
    labs(
      title = paste("Bias by Scenario and Model (num_var =", nv, ")"),
      x = "Scenario",
      y = "Bias"
    )
  print(p)
}
```

### Plotting the Heatmap, does not perform well here though
```{r}
unique_numvar <- unique(df_master$num_var)

for (nv in unique_numvar) {
  df_temp <- df_master %>% filter(num_var == nv)
  
  p <- ggplot(df_temp, aes(x = scenario, y = model, fill = mse_ratio)) +
    geom_tile(color = "white") +
    facet_wrap(~ scenario10_num_var, ncol = 1) +
    scale_fill_gradient(low = "white", high = "blue") +
    labs(
      title = paste("MSE Ratio Heatmap (num_var =", nv, ")"),
      x = "Scenario",
      y = "Model",
      fill = "MSE Ratio"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  print(p)
}

```
## Justin's edits for report purposes

### Plotting the Bias by Scenario and Model for each number of variables
```{r}
# Ensure scenario is a factor
df_master <- df_master %>%
  mutate(
    scenario = factor(scenario),
    num_var = factor(num_var, levels = c(5, 10, 25))  # set order if needed
  )

# Rename facet labels
facet_labels <- c(
  "5" = "5 Variables",
  "10" = "10 Variables",
  "25" = "25 Variables"
)

# Combined plot
p <- ggplot(df_master, aes(x = scenario, y = bias_mc, color = model, group = model)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 1.8) +
  facet_wrap(~ num_var, ncol = 1, labeller = labeller(num_var = facet_labels)) +
  scale_y_continuous(limits = c(-4, 4)) +
  labs(
    title = "Bias by Scenario and Model",
    x = "Scenario",
    y = "Bias",
    color = "Model"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.margin = margin(t = 5, b = 5, r = 5, l = 5),            
    legend.box.margin = margin(t = -5),               
    legend.title = element_text(size = 14, face = "bold"),
    legend.text = element_text(size = 12),
    
    strip.text = element_text(size = 11, face = "bold", margin = margin(b = 2)),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14, face = "bold"),
    
    panel.spacing = unit(0.4, "lines"),               
    plot.title = element_text(hjust = 0.5, size = 16, margin = margin(b = 5)),
    plot.margin = margin(t = 5, r = 5, b = 5, l = 5),
    legend.background = element_rect(color = "black", fill = NA, linewidth = 1)
  )

# Show plot
print(p)

ggsave("consolidated_bias_facet_plot_290325.png", plot = p, width = 10, height = 8, dpi = 300)


```

### Plotting the Heatmap to make it prettier
```{r}

# Set a consistent max value for the color scale (e.g., based on full dataset)
max_log_mse <- max(log1p(df_master$mse_ratio), na.rm = TRUE)

# Rename plot labels
facet_labels <- c(
  "5" = "5 Variables",
  "10" = "10 Variables",
  "25" = "25 Variables"
)

# reorder model factor by average performance
model_order <- df_master %>%
  group_by(model) %>%
  summarise(mean_mse = mean(mse_ratio, na.rm = TRUE)) %>%
  arrange(mean_mse) %>%
  pull(model)

df_master$model <- factor(df_master$model, levels = model_order)

# Create the heatmap
p <- ggplot(df_master,aes(x = factor(scenario), y = model, fill = log1p(mse_ratio))) +
  geom_tile(color = "white") +
  # Optional: Add value labels
  # geom_text(aes(label = round(mse_ratio, 1)), size = 3, color = "black") +
  facet_wrap(~ num_var, nrow = 1, labeller = labeller(num_var = facet_labels)) +
  scale_fill_gradient(low = "white", high = "blue", limits = c(0, max_log_mse), na.value = "white") +
  labs(
    title = "Log MSE Ratio Heatmap across Models, Scenarios, and Variable Counts",
    x = "Scenario",
    y = "Model",
    fill = "log(1 + MSE Ratio)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text = element_text(size = 12, face = "bold"),
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold")
  )

print(p)

ggsave("mse_heatmap_290325.png", plot = p, width = 15, height = 6, dpi = 300)

```

### Plotting the Heatmap to make it prettier
```{r}
library(ggplot2)
library(dplyr)
library(plotly)

# Preprocess for custom hover labels
df_master <- df_master %>%
  mutate(model = recode(model,
                         madr = "MADR",
                         sis_lasso = "SiS Lasso",
                         backward_selection = "Backward Selection",
                         sis_glider = "SiS GLiDeR",
                         adaptive_lasso = "Adaptive Lasso",
                         glider = "GLiDeR",
                         rlasso = "rLasso")) %>%
  mutate(
    scenario = factor(scenario),
    log_mse_ratio = log1p(mse_ratio),
    hover_text = paste0(
      "Model: ", model, "<br>",
      "Scenario: ", scenario, "<br>",
      "log(1 + MSE Ratio): ", round(log_mse_ratio, 2), "<br>",
      "Model MSE: ", round(mse_mc, 4), "<br>",
      "Saturated MSE: ", round(saturated_mse_mc, 4)
    )
  )

# Set facet labels
facet_labels <- c("5" = "5 Variables", "10" = "10 Variables", "25" = "25 Variables")

# Set max color scale
max_log_mse <- max(df_master$log_mse_ratio, na.rm = TRUE)

# Reorder model levels
model_order <- df_master %>%
  group_by(model) %>%
  summarise(mean_mse = mean(mse_ratio, na.rm = TRUE)) %>%
  arrange(mean_mse) %>%
  pull(model)

df_master$model <- factor(df_master$model, levels = model_order)

# Base ggplot
p <- ggplot(df_master, aes(x = scenario, y = model, fill = log_mse_ratio, text = hover_text)) +
  geom_tile(color = "white") +
  facet_wrap(~ num_var, nrow = 1, labeller = labeller(num_var = facet_labels)) +
  scale_fill_gradient(low = "white", high = "blue", limits = c(0, max_log_mse), na.value = "white") +
  labs(
    title = "Interactive Log MSE Ratio Heatmap",
    x = "Scenario",
    y = "Model",
    fill = "log(1 + MSE Ratio)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.text = element_text(size = 12, face = "bold"),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold")
  )

# Convert to plotly and set tooltip to use custom hover_text
interactive_plot <- ggplotly(p, tooltip = "text")

# Show interactive plot
interactive_plot

```

### boxplot
```{r}
ggplot(df_master, aes(x = model, y = sd_mc, fill = model)) +
  geom_boxplot() +
  facet_wrap(~ num_var, labeller = labeller(num_var = facet_labels)) +
  labs(
    title = "Distribution of Monte Carlo SD across Scenarios",
    x = "Model",
    y = "MC SD"
  ) +
  theme_minimal()
```

### Violin plot
```{r}
violin = ggplot(df_master, aes(x = model, y = sd_mc, fill = model)) +
  geom_violin(trim = FALSE, alpha = 0.7) +
  facet_wrap(~ num_var, labeller = labeller(num_var = facet_labels)) +
  labs(
    title = "Distribution of Monte Carlo SD across Scenarios",
    x = "Model",
    y = "MC SD",
    fill = "Model"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14, face = "bold"),
    legend.position = "bottom",
    legend.title = element_text(size = 14, face = "bold"),
    legend.text = element_text(size = 12),
    legend.background = element_rect(color = "black", fill = NA, linewidth = 1)
  )

violin

ggsave("mcsd_violin_distribution_290325.png", plot = violin, width = 12, height = 6, dpi = 300)
```
